---
title: "compartment analysis_121522"
format: gfm
editor: visual
---

## Loading library

```{r}
library(tidyverse)
```

## Data analysis for various genes obtained along with their eigen vector

#1 the excel sheet was generated by running the pearl script for compartment analysis #2 the aim for generating the graph was to see how a number of genes are differentially transcribed (active or repressive) in a developmental stage that is mesenchymal stem cell and in a terminally differentiated cell type- adipocyte in this case. #3 geom point was an appropriate choice as it represents all the genes on the y axis and the genes expressed in MSC in black and those same genes eigen vector values in purple.

```{r}
adipo_down <- read.csv("table_adi_down_micro_RNAseq_short.csv")


 ggplot(adipo_down, aes(x= MSC.D0.R1_diff, y= name), size = 2)+
geom_point()+
 
   geom_point(data = adipo_down, aes(x = Adipo.D15.R1_Hao_diff, 
                              y = name), 
              color = "purple", shape = "square", size = 2) +
   theme_bw() +
   theme(panel.grid.major = element_blank()) +
   theme(panel.grid.minor = element_blank())
```
