---
title: "compartment_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{compartment_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(finalproject)
```


The following code uses the bedgraph file produced by the alignment code in this package. It will be named "Fastq.sorted.bg". If you want to run this code on a previously produced bedgraph file, replace "Fastq.sorted.bg" with your file name. 

```{perl}
inclusive_bedGraph.load_chrom_data('Fastq.sorted.bg')


    perl/sw/cs400_centos7.3_acfsoftware/
      cworld-dekker/new/centos7.3_gnu6.3.0/
      cworld-dekker-master/scripts/perl/
      fastq.sorted.bg.scalemartix.p1 ^c
    
    
    perl/sw/cs400_centos7.3_acfsoftware/
      cworld-dekker/new/centos7.3_gnu6.3.0/
      cworld-dekker-master/scripts/perl/
      fastq.sorted.bg.matrix2compartment.p1 ^c
    

```

The first code chuck helps in forming the matrix from the files received after the alignment

The second code chuck this code converts the matrix generated into the compartments which further gives the eigen vector values which helps in analyzing the data further
